Active Damping of Rotating Platforms using Integral Force Feedback

### 2020-10-26 journal/paper.tex
Add Journal folder for extended publication

% Created 2020-07-09 jeu. 09:06
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc,arrows,arrows.meta}
\date{}
\title{Active Damping of Rotating Platforms using Integral Force Feedback}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Platforms using Integral Force Feedback},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\abstract{
This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
Guaranteed stability, typical benefit of IFF, is lost as soon as the system is rotating due to gyroscopic effects.
To overcome this issue, two modifications of the classical IFF control scheme are proposed.
The first consists of slightly modifying the control law while the second consists of adding springs in parallel with the force sensors.
Conditions for stability and optimal parameters are derived.
The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
}

\section{Introduction}
\label{sec:orgf2d9f1e}
\label{sec:introduction}
There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.

@@

\section{Dynamics of Rotating Platforms}
\label{sec:orgf97884c}
\label{sec:dynamics}
In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:system}Schematic of the studied System}
\end{figure}

@@

\par
To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
\begin{equation}
\label{eq:lagrangian_equations}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
\begin{equation}
\label{eq:energy_functions_lagrange}
  \begin{aligned}
    T & = \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \quad V = \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right),\\
    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
  \end{aligned}
\end{equation}

@@

\par
To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
\begin{align}
  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
  \bm{G}_{d} &=
  \begin{bmatrix}
    \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
    \frac{-2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} & \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2}
  \end{bmatrix} \label{eq:Gd_m_k_c}
\end{align}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\hfill
\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
\end{subfigure}
\hfill
\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
\centering
\end{figure}

\section{Decentralized Integral Force Feedback}
\label{sec:orgf541d3f}
\label{sec:iff}
In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.

\begin{minipage}[t]{0.50\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/system_iff.pdf}
\captionof{figure}{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/control_diagram_iff.pdf}
\captionof{figure}{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
\end{center}
\end{minipage}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filter}
\label{sec:orgf53673d}
\label{sec:iff_hpf}
As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.

@@

\begin{minipage}[b]{0.45\linewidth}
\begin{center}
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\captionof{figure}{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[b]{0.5\linewidth}
\begin{center}
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\captionof{figure}{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{center}
\end{minipage}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\). Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org4c124af}
\label{sec:iff_kp}
In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.

@@

\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
\captionof{figure}{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/cedrat_xy25xs.png}
\captionof{figure}{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
\end{center}
\end{minipage}

@@

\begin{minipage}[b]{0.43\linewidth}
\begin{center}
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\captionof{figure}{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[b]{0.53\linewidth}
\begin{center}
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\captionof{figure}{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{center}
\end{minipage}

@@

\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
\captionof{figure}{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
\end{center}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
\captionof{figure}{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
\end{center}
\end{minipage}

\section{Comparison and Discussion}
\label{sec:org537f1b3}
\label{sec:comparison}
Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_root_locus.pdf}
\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility} Transmissibility}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance} Compliance}
\end{subfigure}
\hfill
\caption{\label{fig:comp_active_damping}Comparison of the two proposed Active Damping Techniques, \(\Omega = 0.1 \omega_0\)}
\centering
\end{figure}

@@

\section{Conclusion}
\label{sec:orga805aaa}
\label{sec:conclusion}

@@

\section*{Acknowledgment}
\label{sec:orge39bf3f}
This research benefited from a FRIA grant from the French Community of Belgium.

>>>>

% Created 2020-10-26 lun. 18:45
% Intended LaTeX compiler: pdflatex
\documentclass[Afour,sagev,times]{sagej}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\usepackage{tikz}
\usetikzlibrary{shapes.misc,arrows,arrows.meta}
\hypersetup{colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red}
\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\def\volumeyear{2016}
\author{Dehaeze Thomas\affilnum{1} and Collette Christophe\affilnum{2}}
\affiliation{\affilnum{1}Precision Mechatronics Laboratory, University of Liege, Belgium\\
\affilnum{2}BEAMS Department, Free University of Brussels, Belgium\\
\affilnum{3}European Synchrotron Radiation Facility, Grenoble, France}
\email{dehaeze.thomas@gmail.com}
\bibliographystyle{SageV}
\begin{abstract}
This paper investigates the use of Integral Force Feedback (IFF) for the active damping of rotating mechanical systems.
Guaranteed stability, typical benefit of IFF, is lost as soon as the system is rotating due to gyroscopic effects.
To overcome this issue, two modifications of the classical IFF control scheme are proposed.
The first consists of slightly modifying the control law while the second consists of adding springs in parallel with the force sensors.
Conditions for stability and optimal parameters are derived.
The results reveal that, despite their different implementations, both modified IFF control scheme have almost identical damping authority on suspension modes.
\end{abstract}
\keywords{active damping, IFF}
\date{}
\title{Active Damping of Rotating Platforms using Integral Force Feedback}
\begin{document}

@@

\section{Introduction}
\label{sec:orgdef8140}
\label{sec:introduction}
There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.

@@

\section{Dynamics of Rotating Platforms}
\label{sec:org392ac57}
\label{sec:dynamics}
In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/system.pdf}
\caption{\label{fig:system}Schematic of the studied System}
\end{figure}

@@

\par
To obtain the equations of motion for the system represented in Figure \ref{fig:system}, the Lagrangian equations are used:
\begin{equation}
\label{eq:lagrangian_equations}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(L = T - V\) the Lagrangian, \(T\) the kinetic coenergy, \(V\) the potential energy, \(D\) the dissipation function, and \(Q_i\) the generalized force associated with the generalized variable \(\begin{bmatrix}q_1 & q_2\end{bmatrix} = \begin{bmatrix}d_u & d_v\end{bmatrix}\).
The equation of motion corresponding to the constant rotation in the \((\vec{i}_x, \vec{i}_y)\) plane is disregarded as the motion is considered to be imposed by the rotation stage.
\begin{equation}
\label{eq:energy_functions_lagrange}
  \begin{aligned}
    T &= \frac{1}{2} m \left( \left( \dot{d}_u - \Omega d_v \right)^2 + \left( \dot{d}_v + \Omega d_u \right)^2 \right), \\
    V &= \frac{1}{2} k \left( {d_u}^2 + {d_v}^2 \right), \\
    D &= \frac{1}{2} c \left( \dot{d}_u{}^2 + \dot{d}_v{}^2 \right), \quad Q_1 = F_u, \quad Q_2 = F_v
  \end{aligned}
\end{equation}

@@

\par
To study the dynamics of the system, the differential equations of motions \eqref{eq:eom_coupled} are transformed in the Laplace domain and the \(2 \times 2\) transfer function matrix \(\bm{G}_d\) from \(\begin{bmatrix}F_u & F_v\end{bmatrix}\) to \(\begin{bmatrix}d_u & d_v\end{bmatrix}\) is obtained
\begin{align}
  \begin{bmatrix} d_u \\ d_v \end{bmatrix} &= \bm{G}_d \begin{bmatrix} F_u \\ F_v \end{bmatrix} \label{eq:Gd_mimo_tf} \\
  \bm{G}_{d}(1,1) &= \frac{ms^2 + cs + k - m \Omega^2}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
                  &= \bm{G}_{d}(2,2) \nonumber \\
  \bm{G}_{d}(1,2) &= \frac{2 m \Omega s}{\left( m s^2 + cs + k - m \Omega^2 \right)^2 + \left( 2 m \Omega s \right)^2} \\
                  &= -\bm{G}_{d}(1,2) \nonumber
\end{align}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\hfill
\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.49\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(-d_u/F_v\)}
\end{subfigure}
\hfill
\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
\centering
\end{figure}

\section{Decentralized Integral Force Feedback}
\label{sec:orgcaa78cf}
\label{sec:iff}
In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/system_iff.pdf}
\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
\caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filter}
\label{sec:org704f416}
\label{sec:iff_hpf}
As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\). Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org1c4a11f}
\label{sec:iff_kp}
In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
\caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/mod_iff_damping_kp.pdf}
\caption{\label{fig:mod_iff_damping_kp}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
\end{figure}

\section{Comparison and Discussion}
\label{sec:orgcd508a8}
\label{sec:comparison}
Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/comp_root_locus.pdf}
\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
\end{figure}

@@

\section{Conclusion}
\label{sec:org6cd163b}
\label{sec:conclusion}

@@

\section*{Acknowledgment}
\label{sec:org7856ac4}
This research benefited from a FRIA grant from the French Community of Belgium.
